### 2011-02-21 trunk/deliverables/D4_3/fast_d4_3_2.tex
incorporating Albert's changes
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@1218 d8b0c59b-6544-0410-94d9-83a5658a058e
Added subsection 3.6 discussing other approaches to service wrapping.
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@1274 d8b0c59b-6544-0410-94d9-83a5658a058e

\documentclass{fast_latex}
% yay! We can use any kind of funky diacritic:
\usepackage[utf8]{inputenc}

@@

\begin{small}
\begin{tabular}{|l|l|l|p{7.5cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{\textbf{Rev. No.}} &
                            \textcolor{white}{\textbf{Date}} &
                            \textcolor{white}{\textbf{Author (Partner)}} &
							\textcolor{white}{\textbf{Change description}}\\ \hline
%0.1 & 15.12.2008 & Knud M\"oller (NUIG) & template modelled \\ \hline
%0.2 & 15.02.2009 & Knud M\"oller (NUIG) & content moved from wiki after internal review \\ \hline
1.0 & 26.02.2010 & Ismael Rivera (NUIG), Albert Zündorf (UniKas) & Final version ready for external review \\ \hline
\end{tabular}
\end{small}

@@

@@

\clearpage
\bibliographystyle{apalike}
\addcontentsline{toc}{section}{References}
\bibliography{fast_d4_3_2}

>>>>

\documentclass{article}

\usepackage{fast_latex}
% yay! We can use any kind of funky diacritic:
\usepackage[utf8]{inputenc}

@@

\begin{small}
\begin{tabular}{|l|l|l|p{7.5cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{\textbf{Rev. No.}} &
                            \textcolor{white}{\textbf{Date}} &
                            \textcolor{white}{\textbf{Author (Partner)}} &
							\textcolor{white}{\textbf{Change description}}\\ \hline
%0.1 & 15.12.2008 & Knud M\"oller (NUIG) & template modelled \\ \hline
%0.2 & 15.02.2009 & Knud M\"oller (NUIG) & content moved from wiki after internal review \\ \hline
1.0 & 26.02.2011 & Ismael Rivera (NUIG), & Final version ready for external review \\ 
 & & Albert Zündorf (UniKas) & \\ \hline
\end{tabular}
\end{small}

@@

\subsection{Other approaches} % (fold)
\label{sub:other_approaches}

There is a number of related work that we have consider to use for service wrapping instead of building a Service Wrapper
Tool ourself. However, due to the special needs of the Gadget Development Process it turned out that we were not able 
to use an existing approach directly but we were only able to grab 
ideas from existing approaches and come up with our own implementation. 
As discussed, service wrapping requires three steps. First we have to define the connection between the desired service wrapper and the other building blocks of FAST. This is achieved by the definition of pre- and postconditions in our tool. Since this is very FAST specific, finding an existing tool for this purpose did not work. However, this is a simple step anyhow requiring only 
limited implementation efforts.

Second, we have to construct the request and to send it to the target service. There is already a number of REST clients 
for this purpose. There are even web based REST clients that may be used in a browser. We could easily have used such 
a standard REST client. However, we considered the user interfaces of these REST clients as too complicated for our
end users. In addition, we wanted an easy and simple connection to the pre- and postconditions of the service wrapper. 
This required the integration of a template expansion mechanism into the REST client which was most easy to achieve 
with a new interface build by ourself. Again the effort for this step was limited and justified by the smooth integration into 
the overall tool.

Third, we needed a data mediation step. This might have been achieved by e.g. XSLT tools. XSLT tools work on 
XML input and provide a template based generation of textual output. The problem with XSLT is a quite 
complex syntax which is not adequate for our end users. It would also have been difficult to provide our end users 
with direct feedback, as required by FAST's  storyboard philosophy. Similarly, interactive help e.g. by selection boxes for target 
types and target attribute name would not have been possible, easily. Instead of XSLT we might also have used model based transformation languages like ATL (Atlas Transformation Language) or TGGs (Triple Graph Grammars). While these 
approaches work on a higher level of abstraction compared to XSLT, we still consider them too complicated for our end users. 
In addition, it would have been rather difficult to achieve an integrated interactive support as we have achieved in our 
own implementation. However, our translation rules are heavily influenced by TGGs which was a tremendous help 
for coming up with a simple and easy to use yet powerful approach.

% subsection Other approaches (end)

@@

\clearpage
\bibliographystyle{apalike}
\addcontentsline{toc}{section}{References}
\bibliography{fast_d4_3}
